PineAPPL:\\ combining EW and QCD corrections for PDF fits

### 2020-08-13 paper/paper.tex
Abstract

\abstract{We introduce \textsc{PineAPPL}, a computer library allowing to produce fast-in\-ter\-po\-la\-tion
grids for fitting parton distribution functions (PDFs)
including corrections of strong and electroweak origin. After presenting
the features and performance of such a code, we show how to interface \textsc{PineAPPL} with general-purpose
softwares that allow the user to compute such corrections, providing an explicit example with
\textsc{MadGraph5\_aMC@NLO}. We showcase some phenomenological result focusing on processes and observables
relevant for PDF fits, and 
we discuss what steps need to be undertaken in the presentation of experimental data in order to have them
consistently employed in a fit including electroweak corrections.}

>>>>

\abstract{We introduce \textsc{PineAPPL}, a library that produces
  fast-interpolation grids of physical cross sections, computed with a 
  general-purpose Monte Carlo generator, accurate to fixed order in the
  strong, electroweak, and combined strong-electroweak couplings. We
  discuss its features in comparison to similar software
  available in the literature, and we explicitly interface it to
  \textsc{MadGraph5\_aMC@NLO}. We validate the performance of \textsc{PineAPPL}
  by computing fast-interpolation grids, accurate to next-to-leading order in
  the strong and electroweak couplings, for a representative set of processes
  commonly used in the determination of the parton distribution functions (PDFs)
  of the proton. We formulate a recommendation on the format of the experimental
  deliverables in order to consistently incorporate them in forthcoming
  fits of PDFs including electroweak corrections.}
